What Can Stack Traces Tell us about of the use Exceptions in Java?

### 2014-07-11 android-stacks.tex
changing java and CLU description

Both Java [ref: Gosling et al. 1996] and CLU [Liskov and Snyder 1979] support the declaration of exceptions
 in method signatures, hence the compiler can then check if handlers are provided to such exceptions.
 However, this support is only partial because both languages also provides a form of unchecked exceptions.
In CLU,  if a handler is found for a given exception, it is converted in a predened default exception, 
called failure which is the only one which can be implicitly propagated in this model [ref-clue].
 Java allows a hybrid approach on which the developer can define specific exceptions of both kinds 
(checked or unchecked) to be thrown and handled inside the system.
Therefore, in both languages the developer of a client module is not warned by the compiler of the possibility of 
an unchecked exception being thrown.

>>>>

Both Java [ref: Gosling et al. 1996] and CLU [Liskov and Snyder 1979] support the checked exceptions,
 hence the compiler can then check if handlers are provided to such exceptions.
 However, this support is only partial because both languages also provides a form of unchecked exceptions.
In CLU,  if a handler is found for a given exception, it is converted in a predened default exception, 
called failure which is the only one which can be implicitly propagated [ref-clue].
 Java allows a hybrid approach on which the developer can define specific unchecked and checked exceptions,
and use both kinds of exceptions inside a single system.
In both languages the developer of a client module is not warned by the compiler if 
 unchecked exceptions are thrown by a module.
